\bf An Empirical Comparison of Parametric and Permutation Tests for Regression Analysis of Randomized Experiments

### 2018-03-21 ms/ms.tex
missing period

The goal of a randomized experiment is to draw causal inferences about the efficacy of a treatment.
Thus, it makes sense to analyze experiments in the context of potential outcomes, where every individual has a counterfactual outcome for each of the treatments (\cite{holland_1986_statistics})
Experiments are an attempt to estimate the counterfactual outcomes by randomly assigning treatments.
Random assignment of treatment ensures that pretreatment covariates are balanced between treatment groups on average, across all possible randomizations, making treatment groups comparable to each other.

>>>>

The goal of a randomized experiment is to draw causal inferences about the efficacy of a treatment.
Thus, it makes sense to analyze experiments in the context of potential outcomes, where every individual has a counterfactual outcome for each of the treatments (\cite{holland_1986_statistics}).
Experiments are an attempt to estimate the counterfactual outcomes by randomly assigning treatments.
Random assignment of treatment ensures that pretreatment covariates are balanced between treatment groups on average, across all possible randomizations, making treatment groups comparable to each other.
